### 2015-01-20 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012 Updated Files

\headerB{
Delaware County, PA Fire Suppression Tests \\
Spring 2012 \\
}

@@

@@

@@

@@

Total heat flux was measured with Schmidt Boelter gauges.  Radiant heat flux was measured with Schmidt Boelter gauges with sapphire lens.  One of each was located near the thermocouple arrays in the burn room.  The gauges were pointed at the ceiling and positioned 0.15 m (6 in) above the floor.

>>>>

\headerB{
Examination of Compressed Air Foam (CAF) for Interior Firefighting \\
Spring 2012 \\
}

@@

Traditionally, fire fighting suppression operations have been conducted from the interior of the structure as a means to reduce water damage, manage the “thermal balance,” and limit fire damage to structures.  In current fire fighter training manuals, it is stated that these operations must be coordinated with the ventilation operations.  However guidance on that coordination has been limited.  Previous research and examinations of line of duty deaths have shown that ventilation events occurring with fire fighters in the structure prior to suppression have led to tragic results.  One means of reducing the possibilities of this occurrence would be to begin to extinguish the fire prior to entering the structure.  In effect, an offensive, exterior fire attack, in which water is directed into the structure from the exterior to cool the fire gases and reduce the heat release rate of the fire, prior to the fire fighters entering the building.  The major concern with this type of operation is the potential harm that might occur to people trapped in the structure or the amount of water damage to the structure.  Therefore, measurements are needed to document the changes of the thermal environment within the structure due to interior and exterior fire suppression tactics.  This report will focus on water distribution and fire suppression experiments conducted to develop a baseline for the interior fire suppression.

@@

3)  Examine the impact of solid streams, straight streams, and fog streams on the

@@

The Engineering Laboratory at National Institute of Standards and Technology has a research program aimed at improving the safety and effectiveness of firefighters through improved knowledge of fire behavior and firefighting tactics.  One of the objectives of this program is to examine non-traditional means of fire suppression.   This series of experiments conducted by NIST for the California Polytechnic State University, San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service complements the NIST research program on firefighting tactics.  These experiments are part of a larger research project led by Cal Poly with the purpose of investigating the capabilities and limitations of compressed air foam systems (CAFS) for structural firefighting with the objective of enhancing the scientific knowledge base regarding the effectiveness and safety implications associated with the use of CAFS for structural firefighting.  
NIST conducted several series of experiments to provide scientific measurements and comparisons between CAFS and water-only hose streams for different compartment fire scenarios.  
Three types of experiments were conducted; 
1)            spray density measures under non-fire conditions 
2)            gas layer cooling 
3)            fire suppression in an experimental structures

The key measures were to understand the cooling and suppression capabilities of CAFS compared to water.   The experimental designs were developed based on a project planning workshop which included the discussion of incidents where firefighters had concerns or experienced minor burns while using CAFS during interior attack operations in residential occupancies.  [REF-  PROJECT ON “CAPABILITIES AND LIMITATIONS OF COMPRESSED AIR FOAM SYSTEMS (CAFS) FOR STRUCTURAL FIREFIGHTING” WORKSHOP SUMMARY, December, 13-14, 2011.   Casey C. Grant, P.E., Fire Protection Research Foundation, One Batterymarch Park, Quincy, MA USA 02169-7471
17 January 2012]

Since Montgomery County (MD) Fire and Rescue Service provided the CAFS equipped engines and the staffing needed to provide both the water and CAF for the experiments.  Baseline operating conditions were agreed upon at the workshop for these experiments.

*Nozzles – Metro 1, fixed gallonage fog/straight/7/8”solid stream  
100 feet of hose line – 1-3/4”
Foam concentration – 0.3%
CAF Flowrate – 120 gpm / 60 cfm 
Water / air pressure (100-120 psi)

2.3. Study objective
2.3.1. FF exposure – usability / safety
2.3.1.1. Steam blowback
2.3.1.2. Knockdown time
2.3.1.3. Smoke scrubbing
2.3.1.4. Rekindle time / prevention
2.3.1.5. Overhaul / exposure time
2.3.2. Other Issues
2.3.2.1. Structural fire testing
2.3.2.2. Room / attic configuration

These experiments were conducted at the Delaware County (PA) Emergency Services Training Center (ESTC) in Sharon Hill, PA.

@@

Total heat flux was measured with Schmidt-Boelter gauges.  Radiant heat flux was measured with Schmidt Boelter gauges with sapphire lens.  One of each was located near the thermocouple arrays in the burn room.  The gauges were pointed at the ceiling and positioned 0.15 m (6 in) above the floor.
